Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-07 paper.tex
udapte

The Corona-virus warning app
%has taken a long time to develop being published only on
%16th June 2020. It
was a quite costly project but this was mainly due to the management of
Telekom and SAP being in the driving seat. But the app has been designed with great
attention on privacy:  a distributed architecture \cite{} has been adopted after a long and
heated debate with supporters of a central architecture. The distributed architecture is
based on a very clever distributed application design whereby users phones are sending
highly anonymized so called ``Ephemeral IDs'' at physical locations via the Bluetooth
protocol. The app saves those IDs of people in close proximity. When at a later date an
infected person reports his infection to a central server, the unique root ID is published
and in the daily check all mobile phones connecting to the central server can download
the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
all Ephemeral IDs that have been saved over the last 14 days allow users phones to
regularly check whether their user has been exposed to an infected person and issue
a warning to the user. The warning issued by the Corona warning app entitles to
having a Corona test done (which at the time of writing is not normally possible).

@@

\section{Background and related work}

\subsection{DP-3T and PEPP-PT}
\label{sec:history}
This paper is mainly concerned with the architecture and protocols proposed by the
Decentralized Privacy-Preserving Proximity Tracing project (DP-3T).
The main reason to focus on this particular family of protocols is the
\textit{Exposure Notification Framework}, jointly published by Apple and Google, that adopts
the main core principles of the DP-3T proposal. This API is not only used in the German
Corona-virus warning app but has the potential of being widely adopted in future
app developments that might emerge due to the reach of players like Apple and Google.

@@

\subsubsection{Basic DP-3T protocol: How does it work? How does it relate to ENF/CWA? (broad strokes)}
%
Upon installation,the app generates secret daily seeds to derive so called \textit{Ephemeral IDs}
(EphIDs) from them. EphIDs are generated locally with cryptographic methods and cannot be connected
to one another but only reconstructed from the secret seed they were derived from.

@@

\section{Conclusions}
\label{sec:concl}

>>>>

The Corona-virus warning app
%has taken a long time to develop being published only on
%16th June 2020. It
was a quite costly project but this was mainly due to the management of
Telekom and SAP being in the driving seat. But the app has been designed with great
attention on privacy:  a distributed architecture \cite{} has been adopted after a long and
heated debate with supporters of a central architecture. The distributed architecture is
based on a very clever distributed application design whereby users phones are sending
highly anonymized so called ``Ephemeral IDs'' at physical locations via the Bluetooth
protocol. The app saves those IDs of people in close proximity. When at a later date an
infected person reports his infection to a central server, the unique root ID is published
and in the daily check all mobile phones connecting to the central server can download
the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
all Ephemeral IDs that have been saved over the last 14 days allow users phones to
regularly check whether their user has been exposed to an infected person and issue
a warning to the user. The user then needs to contact health autohorities.
%The warning issued by the Corona warning app entitles to
%having a Corona test done (which at the time of writing is not normally possible).

@@

\section{Background and related work}
\label{sec:background}
\subsection{DP-3T and PEPP-PT}
\label{sec:history}
This paper is mainly concerned with the architecture and protocols proposed by the
Decentralized Privacy-Preserving Proximity Tracing project (DP-3T).
The main reason to focus on this particular family of protocols is the
\textit{Exposure Notification Framework}, jointly published by Apple and Google, that adopts
the main core principles of the DP-3T proposal. This API is not only used in the German
Corona-virus warning app but has the potential of being widely adopted in future
app developments that might emerge due to the reach of players like Apple and Google.

@@

\subsubsection{Basic DP-3T protocol: How does it work?}
%  How does it relate to ENF/CWA? (broad strokes)}
%
Upon installation, the app generates secret daily seeds to derive so called \textit{Ephemeral IDs}
(EphIDs) from them. EphIDs are generated locally with cryptographic methods and cannot be connected
to one another but only reconstructed from the secret seed they were derived from.

@@

\section{Conclusions}
\label{sec:concl}
\subsection{Protection goals of attacks}

\subsection{Relevance of the approach}
